## Example Dataset

::: {.columns .v-center-container}
::: {.column width="40%"}
-   The `trial` data set is included with {gtsummary}

-   Simulated data set of baseline characteristics for 200 patients who receive Drug A or Drug B

-   Variables were assigned labels using the `labelled` package
:::

::: {.column width="60%"}
```{r}
#| label: 'describe-trial'
#| message: false
library(gtsummary)
library(tidyverse)
head(trial) |> gt::gt()
```
:::
:::

## Example Dataset

::: {.columns .v-center-container}
::: {.column width="60%"}
This presentation will use a subset of the variables.

```{r}
#| label: 'create-small-trial'
sm_trial <-
  trial |> 
  select(trt, age, grade, response)
```
:::

::: {.column width="40%"}
```{r}
#| echo: false
#| label: 'describe-small-trial'
tibble(
  Variable = names(sm_trial),
  Label = map_chr(Variable, ~attr(trial[[.x]], "label"))
) |> 
  gt::gt()
```
:::
:::

## Exercise 1

As an exercise, we'll prepare data, data summaries, analyses, and a brief write-up of the results.

1.  Download zip file with exercises with [this link](https://github.com/ddsjoberg/clinical-reporting-gtsummary-rmed/raw/main/exercises/exercises.zip).

2.  Extract the zip file locally and open in an RStudio project. You can unzip the file with your system utilities, or with `zip::unzip()`. Unzip the files into their own folder!

3.  Add variable labels to the data frame using `labelled::set_variable_labels()`.

```{r}
#| echo: false
#| cache: false
countdown(minutes = 8, font_size = "1.5em")
```
