# inline_text()

## {gtsummary} reporting with inline_text()

-   Tables are important, but we often need to report results in-line in a report.

-   Any statistic reported in a {gtsummary} table can be extracted and reported in-line in an R Markdown document with the `inline_text()` function.

-   The pattern of what is reported can be modified with the `pattern =` argument.

-   Default is `pattern = "{estimate} ({conf.level*100}% CI {conf.low}, {conf.high}; {p.value})"`.

## {gtsummary} reporting with inline_text()

```{r}
#| echo: false
tbl_uvreg
```

**In Code:** The odds ratio for age is `` `r "\u0060r inline_text(tbl_uvreg, variable = age)\u0060"` ``

**In Report:** The odds ratio for age is `r inline_text(tbl_uvreg, variable = age)`

## Exercise 5

Write a brief summary of the results above using `inline_text()` to report values from the tables directly into the markdown report.

1. Report at least one statistic from the cohort summary.

1. Report the difference in death rates.

1. Report the odds ratio for death from the multivariable logistic regression model.

```{r echo=FALSE}
countdown(minutes = 8, font_size = "1.5em")
```