# inline_text()

## {gtsummary} reporting with inline_text()

-   Tables are important, but we often need to [report results in-line]{.emphasis}.

-   Any statistic reported in a {gtsummary} table can be extracted and reported in-line in an R Markdown document with the `inline_text()` function.

-   The pattern of what is reported can be modified with the `pattern=` argument.

-   Default is `pattern = "{estimate} ({conf.level*100}% CI {conf.low}, {conf.high}; {p.value})"` for regression summaries.

## {gtsummary} reporting with inline_text()

```{r}
#| echo: false
tbl_uvreg
```

**In Code:** The odds ratio for age is `` `r "\u0060r inline_text(tbl_uvreg, variable = age)\u0060"` ``

**In Report:** The odds ratio for age is `r inline_text(tbl_uvreg, variable = age)`

## {gtsummary} reporting with inline_text()

```{r}
#| output-location: "column"
gts_small_summary <-
  trial %>% 
  tbl_summary(
    by = trt,
    include = marker,
    missing = "no"
  ) %>%
  add_difference()
gts_small_summary
```

::: columns
::: {.column width="78%"}
::: {.small}
**In Code:** 

- The median (IQR) marker among participants randomized to Drug A was `` `r "\u0060r inline_text(gts_small_summary, variable = marker, column = 'Drug A')\u0060"` ``.
- The median (IQR) age among participants randomized to Drug A was `` `r "\u0060r inline_text(gts_small_summary, variable = marker, column = 'Drug A', pattern = '{median}')\u0060"` ``.
- The difference in marker level was `` `r "\u0060r inline_text(gts_small_summary, variable = marker, pattern = '{estimate} (95% {ci})')\u0060"` ``.
:::
:::

::: {.column width="22%"}
::: {.smaller}
**In Report:** 

- The median (IQR) marker among participants randomized to Drug A was `r inline_text(gts_small_summary, variable = marker, column = "Drug A")`.
- The median (IQR) age among participants randomized to Drug A was `r inline_text(gts_small_summary, variable = marker, column = "Drug A", pattern = "{median}")`.
- The difference in marker level was `r inline_text(gts_small_summary, variable = marker, pattern = "{estimate} (95% {ci})")`.
:::
:::
:::





## Exercise 5

Write a brief summary of the results above using `inline_text()` to report values from the tables directly into the markdown report.
You'll likely need `gtsummary::show_header_names()`.

1. Report at least one statistic from the cohort summary. 

1. Report the difference in death rates. 

1. Report the odds ratio for death from the multivariable logistic regression model.

```{r}
#| echo: false
#| cache: false
countdown(minutes = 8)
```