# {gtsummary} themes

## {gtsummary} theme basics

- A **theme** is a set of customization preferences that can be easily set and reused. 

- Themes control **default settings for existing functions**

- Themes control more **fine-grained customization** not available via arguments or helper functions

- Easily use one of the **available themes**, or **create your own**

## {gtsummary} default theme

```{r}
#| output-location: "column"
reset_gtsummary_theme()
m1 |>
  tbl_regression(
    exponentiate = TRUE
  ) |>
  modify_caption(
    "Default Theme"
  )
```

## {gtsummary} theme_gtsummary_journal()

```{r}
#| output-location: "column"
reset_gtsummary_theme()
theme_gtsummary_journal(journal = "jama")

m1 |>
  tbl_regression(
    exponentiate = TRUE
  ) |>
  modify_caption(
    "Journal Theme (JAMA)"
  )
```

*Contributions welcome!*

## {gtsummary} theme_gtsummary_language()

```{r}
#| output-location: "column"
reset_gtsummary_theme()
theme_gtsummary_language(language = "zh-tw")

m1 |>
  tbl_regression(
    exponentiate = TRUE
  ) |>
  modify_caption(
    "Language Theme (Chinese)"
  )
```

Language options: "de" (German), "en" (English), "es" (Spanish), "fr" (French), "gu" (Gujarati), "hi" (Hindi), "is" (Icelandic), "ja" (Japanese), "kr" (Korean), "mr" (Marathi), "nl" (Dutch), "no" (Norwegian), "pt" (Portuguese), "se" (Swedish), "zh-cn" (Chinese Simplified), "zh-tw" (Chinese Traditional)

## {gtsummary} theme_gtsummary_compact()

```{r}
reset_gtsummary_theme()
theme_gtsummary_compact()

tbl_regression(m1, exponentiate = TRUE) |>
  modify_caption("Compact Theme")
```

*Reduces padding and font size*

## {gtsummary} set_gtsummary_theme()


* `set_gtsummary_theme()` to use a custom theme.

* See the {gtsummary} + themes vignette for examples

[http://www.danieldsjoberg.com/gtsummary/articles/themes.html](http://www.danieldsjoberg.com/gtsummary/articles/themes.html)
