# {gtsummary} themes

## {gtsummary} theme basics

- A [theme]{.emphasis} is a set of customization preferences that can be easily set and reused. 

- Themes control [default settings for existing functions]{.emphasis}

- Themes control more [fine-grained customization]{.emphasis} not available via arguments or helper functions

- Easily use one of the [available themes]{.emphasis}, or [create your own]{.emphasis}

## {gtsummary} default theme

```{r}
#| output-location: "column"
reset_gtsummary_theme()
m1 |>
  tbl_regression(
    exponentiate = TRUE
  ) |>
  modify_caption(
    "Default Theme"
  )
```

## {gtsummary} theme_gtsummary_journal()

```{r}
#| output-location: "column"
reset_gtsummary_theme()
theme_gtsummary_journal(journal = "jama")

m1 |>
  tbl_regression(
    exponentiate = TRUE
  ) |>
  modify_caption(
    "Journal Theme (JAMA)"
  )
```

*Contributions welcome!*

## {gtsummary} theme_gtsummary_language()

```{r}
#| output-location: "column"
reset_gtsummary_theme()
theme_gtsummary_language(language = "zh-tw")

m1 |>
  tbl_regression(
    exponentiate = TRUE
  ) |>
  modify_caption(
    "Language Theme (Chinese)"
  )
```

**Language options:**

:::{.columns style="font-size:0.65em"}
::: {.column width="30%"}

- German 
- English
- Spanish 
- French 
- Gujarati
- Hindi

::: 

::: {.column width="30%"}
- Icelandic
- Japanese
- Korean
- Marathi
- Dutch

:::

::: {.column width="30%"}
- Norwegian
- Portuguese
- Swedish
- Chinese Simplified
- Chinese Traditional
:::
:::

## {gtsummary} theme_gtsummary_compact()

```{r}
reset_gtsummary_theme()
theme_gtsummary_compact()

tbl_regression(m1, exponentiate = TRUE) |>
  modify_caption("Compact Theme")
```

*Reduces padding and font size*

## {gtsummary} set_gtsummary_theme()


* `set_gtsummary_theme()` to use a custom theme.

* See the {gtsummary} + themes vignette for examples

[http://www.danieldsjoberg.com/gtsummary/articles/themes.html](http://www.danieldsjoberg.com/gtsummary/articles/themes.html)
