---
title: "Clinical Reporting with gtsummary"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Solution available at https://www.danieldsjoberg.com/clinical-reporting-gtsummary-rmed/exercises/solutions.html

# Exercise 1

### The Data

Using the National Health and Nutrition Examination Survey Data (`nhefs`), we will assess whether quitting smoking leads to a decrease in the risk of death. We'll also investigate potential confounding factors--age, sex, blood pressure, diabetes, and exercise.

To begin, let's pare down the data frame and assign column labels.

```{r data_prep}
library(gtsummary)
library(tidyverse)
theme_gtsummary_compact()

df_nhefs <-
  causaldata::nhefs %>%
  select(death, qsmk, age, sex, sbp, dbp, exercise) %>%
  drop_na() %>%
  mutate(
    qsmk =
      factor(
        qsmk,
        levels = 0:1,
        labels = c("Did not Quit", "Quit")
      ),
    sex = 
      case_when(
        sex == 0 ~ "Male",
        sex == 1 ~ "Female"
      ),
    exercise = 
      factor(
        exercise,
        levels = 0:2,
        labels = c("Much exercise", "Moderate exercise", "Little or no exercise")
      ) %>%
      fct_rev()
  ) %>%
  labelled::set_variable_labels(
    # >>>> ADD VARIABLE LABELS HERE <<<< 
  )

skimr::skim(df_nhefs)
```

# Exercise 2

Prepare a table describing the cohort by whether or not the participant quit smoking. Do not include death in the summary table. Consider using the gtsummary functions that build on a summary table.

```{r cohort_desc}

```

# Exercise 3

Is there a difference in death rates by smoking status?

Prepare an unadjusted and adjusted rate difference in the table.

```{r death_rate_diff}
# Visit https://www.danieldsjoberg.com/gtsummary/reference/tests.html for a listing of included tests.
# Tests that make use of the `add_difference(adj.vars=)` argument are adjusted analyses.
```

# Exercise 4

Build a logistic regression model with death as the outcome. Include smoking and the other variables as covariates. Summarize your regression model in a table, reporting the odds ratios, confidence intervals, and p-values.

```{r regression}

```

# Exercise 5

Write a brief summary of the results above using `inline_text()` to report values from the tables directly into the markdown report.

```{r inline}
# >>>> USE inline_text() TO DEFINE A FEW STATISTICS TO REPORT IN THE TEXT BELOW <<<<
```

------------------------------------------------------------------------

WRITE A SUMMARY OF THE RESULTS REPORTING STATISTICS FROM `inline_text()`.