---
title: "Clinical Reporting with gtsummary: Solutions"
format: html
---

# Exercise 1

### The Data

Using the National Health and Nutrition Examination Survey Data (`nhefs`), we will assess whether quitting smoking leads to a decrease in the risk of death. We'll also investigate whether potential confounding factors--age, sex, blood pressure, diabetes, and exercise.

To begin, let's pare down the data frame and assign column labels.

```{r data_prep}
library(gtsummary)
library(tidyverse)
theme_gtsummary_compact()

df_nhefs <-
  causaldata::nhefs %>%
  select(death, qsmk, age, sex, sbp, dbp, exercise) %>%
  drop_na() %>%
  mutate(
    qsmk =
      factor(
        qsmk,
        levels = 0:1,
        labels = c("Did not Quit", "Quit")
      ),
    sex = 
      case_when(
        sex == 0 ~ "Male",
        sex == 1 ~ "Female"
      ),
    exercise = 
      factor(
        exercise,
        levels = 0:2,
        labels = c("Much exercise", "Moderate exercise", "Little or no exercise")
      ) %>%
      fct_rev()
  ) %>%
  labelled::set_variable_labels(
    death = "Participant Passed Away",
    qsmk = "Quit Smoking",
    age = "Age",
    sex = "Sex",
    sbp = "Systolic BP",
    dbp = "Diastolic BP",
    exercise = "Exercise Level"
  )

skimr::skim(df_nhefs)
```

# Exercise 2

Prepare a table describing the cohort by whether or not the participant quit smoking. Do not include death in the summary table. Consider using the gtsummary functions that build on a summary table.

```{r cohort_desc}
gts_patient_characteristics <-
  df_nhefs %>%
  tbl_summary(
    by = qsmk,
    include = -death
  ) %>%
  add_p() %>%
  add_stat_label() %>%
  modify_spanning_header(
    all_stat_cols() ~ "**Smoking Status**"
  )
gts_patient_characteristics
```

# Exercise 3

Is there a difference in death rates by smoking status?

Prepare an unadjusted and adjusted rate difference in the table.

```{r death_rate_diff}
# Visit https://www.danieldsjoberg.com/gtsummary/reference/tests.html for a listing of included tests.
# Tests that make use of the `add_difference(adj.vars=)` argument are adjusted analyses.

gts_death_unadjusted <-
  df_nhefs %>%
  tbl_summary(
    by = qsmk, 
    include = death,
    statistic = all_categorical() ~ "{p}%"
  ) %>%
  add_difference() %>%
  add_stat_label() 
gts_death_unadjusted

gts_death_adjusted <-
  df_nhefs %>%
  tbl_summary(
    by = qsmk, 
    include = death,
    statistic = all_categorical() ~ "{p}%"
  ) %>%
  add_difference(
    test = all_categorical() ~ "emmeans",
    adj.vars = c(age, sex, sbp, dbp, exercise)
  ) %>%
  add_stat_label() 
gts_death_adjusted
```

# Exercise 4

Build a logistic regression model with death as the outcome. Include smoking and the other variables as covariates. Summarize your regression model in a table, reporting the odds ratios, confidence intervals, and p-values.

```{r regression}
mod <- glm(death ~ qsmk + age + sex + sbp + dbp + exercise, 
           data = df_nhefs, family = binomial)

gts_mod <-
  tbl_regression(mod, exponentiate = TRUE) %>%
  add_global_p() %>%
  bold_p() %>%
  italicize_levels() %>%
  modify_caption("**Logistic regression model predicting death**") %>%
  modify_header(label = "**Variable** (N = {N})")
gts_mod
```

# Exercise 5

Write a brief summary of the results above using `inline_text()` to report values from the tables directly into the markdown report.

```{r inline}
median_age_quit <-
  inline_text(gts_patient_characteristics, 
              variable = age, 
              column = "Quit", 
              pattern = "{median}")
median_age_no_quit <-
  inline_text(gts_patient_characteristics, 
              variable = age, 
              column = "Did not Quit", 
              pattern = "{median}")
pvalue_age <- 
  inline_text(gts_patient_characteristics, 
              variable = age,
              column = p.value)
unadj_difference <-
  inline_text(gts_death_unadjusted,
              variable = death,
              pattern = "difference {estimate}; 95% CI {ci}; {p.value}")

adj_qsmk_or <-
  inline_text(gts_mod,
              variable = qsmk,
              level = "Quit",
              pattern = "odds ratio {estimate}; 95% CI {ci}")
```

------------------------------------------------------------------------

The analysis assessing the relationship between quitting smoking and subsequent death within the next 20 years included `r nrow(df_nhefs)` participants. The median age among those who quit was higher compared to those who did not (`r median_age_quit` vs `r median_age_no_quit`; `r pvalue_age`).

On univariate analysis, participants who did not quit smoking had higher rates of death (`r unadj_difference`). However, on multivariable analysis, the relationship was not longer significant (`r adj_qsmk_or`).
