---
title: "Reproducible Reporting with {gtsummary}"
author: "Daniel D. Sjoberg"
footer:  "[Reproducible Reporting with {gtsummary}](https://www.danieldsjoberg.com/gtsummary/)"
logo: "img/gtsummary-logo.png"
format: 
  revealjs: 
    theme: [night, slides.scss]
    highlight-style: a11y
    transition: fade
    slide-number: true
    chalkboard: true
execute:
  freeze: auto
---

```{r}
knitr::opts_chunk$set(echo = TRUE, results = 'asis')
library(gtsummary)
library(tidyverse)

knit_print.gtsummary <- function(x, ...) {
  gtsummary::as_gt(x) |> gt::as_raw_html()
}

registerS3method("knit_print", "gtsummary", knit_print.gtsummary)
```

```{r font-awesome-color}
# fill for font awesome icons
fa_fill <- "#C7B41D"
```

# Introduction

## Daniel Sjoberg

`r fontawesome::fa("link", fill = fa_fill)` [danieldsjoberg.com](https://www.danieldsjoberg.com/)

`r fontawesome::fa("twitter", fill = fa_fill)` [\@statistishdan](https://twitter.com/statistishdan)

`r fontawesome::fa("linkedin", fill = fa_fill)` [linkedin.com/in/ddsjoberg/](https://www.linkedin.com/in/ddsjoberg/)

`r fontawesome::fa("github", fill = fa_fill)` [github.com/ddsjoberg](https://github.com/ddsjoberg/)

## Acknowledgements

<br> ADD SOMETHING ABOUT CONFERENCE SPONSERS? <br><br> This work is licensed under a [Creative Commons Attribution-ShareAlike 4.0 International License](https://creativecommons.org/licenses/by-sa/4.0/) (CC BY-SA4.0).

## Checklist

<br>

`r fontawesome::fa("check", fill = fa_fill)` R installed? Pretty recent?

    Current version `r stringr::word(R.version.string, 3, 3)`

`r fontawesome::fa("check", fill = fa_fill)` RStudio installed?

    I am on version 2022.02.3+492 

`r fontawesome::fa("check", fill = fa_fill)` Have these packages?

    {gtsummary} {tidyverse}

```r
install.packages(c("gtsummary", "tidyverse"))
```

## Show a tbl

```{r}
#| output-location: "column-fragment"
trial |> 
  tbl_summary(
    by = trt, 
    include = c(age, grade)
  )
```

